### 2012-09-21 hdf5/discs_2012/evaluation.tex
one change to evaluation. 2) added gary as co-author

Overall, our results show that although the plugin generally shows good performance, it does not scale as well as we increase the number of processes. This is due to the fact that since we are directly making calls to the PLFS API, the metadata overhead seems to be high. We have all processes participating in file open and close operations, which for large problem sizes can add siginificant overhead. Hence, for future work, we plan to use ad\_plfs directly in the plugin which can overcome this performance drawback, since ad\_plfs has collective optimizations in open and close. It should however be noted that MPI libraries like Volpex-MPI~\cite{volpex}, which do not have MPI-IO as part of their MPI library, could make use of a plugin that does not rely on MPI-IO.

>>>>

Overall, our results show that although the plugin generally shows good performance, it does not scale as well as we increase the number of processes. This is due to the fact that since we are directly making calls to the PLFS API, the metadata overhead seems to be high. We have all processes participating in file open and close operations, which for large problem sizes can add siginificant overhead. Hence, for future work, we plan to use ad\_plfs directly in the plugin which can overcome this performance drawback, since ad\_plfs has collective optimizations in open and close. It should however be noted that there are some MPI libraries tailored to suit a specific purpose and which do not provide an implementation for MPI-IO. Such libraries can benefit from using a plugin that does not rely on MPI-IO.
